Response to the defense feedback

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

However, prior static approaches cannot precisely capture the amount of leakage. According to the definition of Shannon entropy, the leakage will be
$$\frac{1}{2^{64}}*\log_{2}\frac{1}{2^{64}} + \frac{2^{64}-1}{2^{64}}
    *\log_{2}\frac{2^{64}-1}{2^{64}} \approx 0\, \mathrm{bits}.$$ Max-entropy is defined from the
number of possible observations. Because the program has two
branches, tools based on max-entropy will report the code has a $\log_2{2} = 1.0$
bit leakage.
Both approaches fail to tell how much information is leaked during the execution
precisely. The problem with existing methods is that they are static-based so
input values and real runtime information are neglected by their approaches.
They assume an attacker runs
the program multiple times with many different or random sensitive inputs. As
shown in Figure~\ref{fig:gap}(a), previous models, both Shannon entropy and max
entropy, give an ``average'' estimate of the information leakage. However, it is
not the typical scenario for an adversary to launch a side-channel attack. When
a side-channel attack happens, the adversary wants to retrieve the sensitive
information, in which case the sensitive information is fixed (e.g., AES keys).
The adversary will run the attack over and over again with fixed input and
guess the value bit by
bit (e.g., Kocher's timing attacks~\cite{kocher1996timing}), as in Figure~\ref{fig:gap}(b). We want to have a
theory for dynamic analysis that if the theory says an attack leaks $x$ bits of
secret information from a side-channel vulnerability, then $x$ should be useful
in estimating the sensitive level of the vulnerability. However, the above
methods all fail in real attack models.
\begin{figure}
    \centering
    \includegraphics[width=.65\columnwidth]{./figures/chapter4/RA.pdf}
    \caption{The gap between real attacks and previous models}\label{fig:gap}
\end{figure}

@@

With the above definition, we have the following mapping between $\beta$,
$K$, $M$, and $O$:
%\vspace*{-0pt}
\begin{displaymath}
    \beta(K, M) \rightarrow O.
\end{displaymath}

@@

In information theory, the mutual information (I) is a measure of the mutual
dependence between two variables. Here we use I to describe the
dependence between original sensitive keys ($K$) and attackers' observations ($O$),
which is defined as

\begin{equation} \label{eq:1}
    I(K;O) = \sum_{k {\in} K}{\sum_{o {\in} O}{p(k, o)\log_2\frac{p(k, o)}{p(k)p(o)}}}
\end{equation}

@@

\begin{equation} \label{eq:2}
    I(K;O) = H(K) - H(K|O)
\end{equation}

@@

We can also calculate the leaked information from the sample code in
Figure~\ref{fig:side-channel}. As the size of input sensitive information is
usually public. The problem of quantifying the leaked information has been
transferred into the problem of estimating the size of input key $|K^o|$ under
the condition $o \in O$. The result is shown in Table~\ref{shtable2}. We can see
that some branches (e.g., A) or traces leak much more information than some others.
These kinds of branches can be vulnerable when an attacker's data is incorporate.
For example, the code will skip some of the calculation if the value is 0 in big
number multiplication.

>>>>

However, prior static approaches cannot precisely capture the amount of leakage. According to the definition of Shannon entropy, the leakage will be
$$\frac{1}{2^{64}}*\log_{2}\frac{1}{2^{64}} + \frac{2^{64}-1}{2^{64}}
    *\log_{2}\frac{2^{64}-1}{2^{64}} \approx 0\, \mathrm{bits}.$$ Max-entropy is defined from the
number of possible observations. Because the program has two
branches, tools based on max-entropy will report the code has a $\log_2{2} = 1.0$
bit leakage.
Both approaches fail to tell how much information is leaked during the execution
precisely. The problem with existing methods is that they are static-based so
input values and real runtime information are neglected by their approaches.
They assume an attacker runs
the program multiple times with many different or random sensitive inputs. As
shown in Figure~\ref{fig:gap}(a), previous methods, both Shannon entropy and max
entropy, give an ``average'' estimate of the information leakage. However, it is
not the typical scenario for an adversary to launch a side-channel attack. When
a side-channel attack happens, the adversary wants to retrieve the sensitive
information, in which case the sensitive information is fixed (e.g., AES keys).
The adversary will run the attack over and over again with fixed input and
guess the value bit by
bit (e.g., Kocher's timing attacks~\cite{kocher1996timing}), as in Figure~\ref{fig:gap}(b). We want to have a
theory for dynamic analysis that if the theory says an attack leaks $x$ bits of
secret information from a side-channel vulnerability, then $x$ should be useful
in estimating the sensitive level of the vulnerability. However, the above
methods all fail in real attack models.
\begin{figure}
    \centering
    \includegraphics[width=.65\columnwidth]{./figures/chapter4/RA.pdf}
    \caption{The gap between real attacks and previous models}\label{fig:gap}
\end{figure}

@@

With the above definition, we have the following mapping between $\beta$,
$K$, $M$, and $O$:

\begin{displaymath}
    \beta(K, M) \rightarrow O.
\end{displaymath}

@@

In information theory, the mutual information ($I$) is a measure of the mutual
dependence between two variables. Here we use $I$ to describe the
dependence between original sensitive keys ($K$) and attackers' observations ($O$),
which is defined as

\begin{equation} \label{eq:1}
    I(K;O) = \sum_{k {\in} K}{\sum_{o {\in} O}{p(k, o)\log_2\frac{p(k, o)}{p(k)p(o)}}},
\end{equation}

@@

\begin{equation} \label{eq:2}
    I(K;O) = H(K) - H(K|O),
\end{equation}

@@

We can also calculate the leaked information from the sample code in
Figure~\ref{fig:side-channel}. As the size of input sensitive information is
usually public. The problem of quantifying the leaked information has been
transferred into the problem of estimating the size of input key $|K^o|$ under
the condition $o \in O$. The result is shown in Table~\ref{shtable2}. We can see
that some branches (e.g., A) or traces leak much more information than some others.
These kinds of branches can be vulnerable when an attacker's data is incorporated.
For example, the code will skip some of the calculation if the value is 0 in big
number multiplication.
